Reconstructing Propositional Proofs in Type Theory

### 2017-10-26 paper/sections/proof-reconstruction.tex
[ paper ] bullet symbol.

In the remainder part of this section, a formal description using
type theory is presented to build definitions and theorems of
functions necessary to reconstruct \Metis' inference rules.

@@

\subsection{Reconstructing \Metis' inference rules}
\label{ssec:emulating-inferences}

@@

\begin{notation}
The function name written in bold font is a \Metis inference rule.
The same function name written in roman letters refers to the proposed
version of the rule.
Each rule proposed has a respective theorem also written in roman letters
that proves its soundness.
\end{notation}

@@

\begin{itemize}
  \item[$\bullet$] $φ$ is the \emph{source} formula from a previous deducted derivation.
  \item[$\bullet$] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
\end{itemize}

>>>>

In the remainder part of this section, a formal description using
type theory is presented to build definitions and theorems of
functions necessary to reconstruct \Metis inference rules.

@@

\subsection{Reconstructing \Metis inference rules}
\label{ssec:emulating-inferences}

@@

\begin{notation}
The function name written in \texttt{typewriter} font refers to
a \Metis inference rule.
The same function name written using \textsf{sans serif} refers to the proposed
version of the rule implemented in \cite{AgdaProp,AgdaMetis}.
\end{notation}

@@

\begin{itemize}
  \item[∙] $φ$ is the \emph{source} formula from a previous deducted derivation.
  \item[∙] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
\end{itemize}
